Notes for Week 2/16/19 - 2/22/19

### 2019-02-22 notes/weekly_notes/2.21.19.NotesForWeek.tex
made one or two changes

\begin{lemma}[Spectral similarity of $r$-graph to grid]
	\label{lem: spectral_similarity_rgraph_grid}
	Fix $r \geq 2 \left(\frac{\log t}{t}\right)^{1/d} + (\frac{1}{t})^{1/d}$, and Let $\ell(t) = \sqrt{d} r t^{1/d} + 2\sqrt{d}(\log t)^{1/d}$. For any $\theta \in \Reals^t$, the following relations hold:
	\begin{equation}
	\label{eqn: spectral_similarity_rgraph_grid}
	\frac{\norm{D_{G_r}\theta}_2}{\ell(t)} \leq \norm{D_{grid}\theta}_2 \leq \norm{D_{G_r}\theta}_2
	\end{equation}
	with probability at least $1 - n^{-\alpha}$ where $\alpha = c_1 (\log n)^{1/2}$ for some constant $c_1 > 0$.
\end{lemma}
\begin{proof}
	We begin by mapping the data $\Zbf$ to the grid points $[\kappa]^d$ in such a way that as little mass as possible is disturbed:
	\begin{lemma}
		\label{lem: mass_transport_mapping}
		There exists a bijective mapping $T: \Zbf \to [\kappa]^d$ for $\kappa = t^{1/d}$ such that
		\begin{equation*}
		\max_{i} \norm{T(z_i) - z_i}_2 \leq C\left(\frac{\log t}{t}\right)^{1/d}
		\end{equation*}
		with probability at least $1 - n^{-\alpha}$ where $\alpha = c_1 (\log n)^{1/2}$ for some constant $c_1 > 0$.
	\end{lemma}
	Hereafter, we assume there exists $T$ such that Lemma \ref{lem: mass_transport_mapping} holds.

@@

	Now, we turn to the first bound. Assume $i \sim j$ in the graph $G_r$. By a similar set of steps to the above, we have
	\begin{equation*}
	\norm{T(z_i) - T(z_j)}_2 \leq 2C\left(\frac{\log t}{t}\right)^{1/d} + r
	\end{equation*}
	As a result, using the simple relation $\norm{x}_1 \leq \sqrt{d} \norm{x}_2$ for any $x \in \Rd$, we have
	\begin{equation*}
	\norm{T(z_i) - T(z_j)}_1 \leq \sqrt{d}(2C\left(\frac{\log t}{t}\right)^{1/d} + r)
	\end{equation*}
	Since each edge in the grid graph is of length $n^{1/d}$, it is easy to see that there exists a path between $T(z_i)$ and $T(z_j)$ in $G_{grid}$, $P(T(Z_i) \to T(Z_j))$ with no more than
	\begin{equation*}
		\frac{\sqrt{d}(2C\left(\frac{\log t}{t}\right)^{1/d} + r)}{t^{1/d}}
	\end{equation*}
	edges. The bound follows by Lemma
	\begin{lemma}[Graph ordering]
	\label{lem: graph_ordering}
	Fix $m \geq 0$. For vertices $V = \set{1, \ldots,m}$, we have
	\begin{enumerate}
		\item $\frac{1}{m - 1}P(1 \to m) \succeq G_{1,m}$
		\item If $A \succeq B$ and $C \succeq D$, then $A + B \succeq C + D$. 
	\end{enumerate}
	\end{lemma}
\end{proof}

>>>>

\begin{lemma}[Spectral similarity of $r$-graph to grid]
	\label{lem: spectral_similarity_rgraph_grid}
	Fix $r \geq 2 \left(\frac{\log t}{t}\right)^{1/d} + (\frac{1}{t})^{1/d}$, and let $\ell(t) = \sqrt{\sqrt{d} r t^{1/d} + 2\sqrt{d}(\log t)^{1/d}}$. For any $\theta \in \Reals^t$, the following relations hold:
	\begin{equation}
	\label{eqn: spectral_similarity_rgraph_grid}
	\frac{\norm{D_{G_r}\theta}_2}{\ell(t)} \leq \norm{D_{grid}\theta}_2 \leq \norm{D_{G_r}\theta}_2
	\end{equation}
	with probability at least $1 - n^{-\alpha}$ where $\alpha = c_1 (\log n)^{1/2}$ for some constant $c_1 > 0$.
\end{lemma}
\begin{proof}
	We begin by mapping the data $\Zbf$ to the grid points $[\kappa]^d$ in such a way that as little mass as possible is disturbed:
	\begin{lemma}
		\label{lem: mass_transport_mapping}
		There exists a bijective mapping $T: \Zbf \to [\kappa]^d$ for $\kappa = t^{1/d}$ such that
		\begin{equation*}
		\max_{i} \norm{T(z_i) - z_i}_2 \leq C\left(\frac{\log t}{t}\right)^{1/d}
		\end{equation*}
		with probability at least $1 - n^{-\alpha}$ where $\alpha = c_1 (\log n)^{1/2}$ for some constant $c_1 > 0$.
	\end{lemma}
	Hereafter, we assume there exists $T$ such that Lemma \ref{lem: mass_transport_mapping} holds.

@@

	Now, we turn to the first bound. Assume $i \sim j$ in the graph $G_r$. By a similar set of steps to the above, we have
	\begin{equation*}
	\norm{T(z_i) - T(z_j)}_2 \leq 2C\left(\frac{\log t}{t}\right)^{1/d} + r
	\end{equation*}
	As a result, using the simple relation $\norm{x}_1 \leq \sqrt{d} \norm{x}_2$ for any $x \in \Rd$, we have
	\begin{equation*}
	\norm{T(z_i) - T(z_j)}_1 \leq \sqrt{d}(2C\left(\frac{\log t}{t}\right)^{1/d} + r)
	\end{equation*}
	Since each edge in the grid graph is of length $n^{1/d}$, it is easy to see that there exists a path between $T(z_i)$ and $T(z_j)$ in $G_{grid}$, $P(T(Z_i) \to T(Z_j))$ with no more than
	\begin{equation*}
		\frac{\sqrt{d}(2C\left(\frac{\log t}{t}\right)^{1/d} + r)}{t^{1/d}}
	\end{equation*}
	edges. The bound follows by Lemma \ref{lem: graph_ordering}.
	\begin{lemma}[Graph ordering]
	\label{lem: graph_ordering}
	Fix $m \geq 0$. For vertices $V = \set{1, \ldots,m}$, we have
	\begin{enumerate}
		\item $\frac{1}{m - 1}P(1 \to m) \succeq G_{1,m}$
		\item If $A \succeq B$ and $C \succeq D$, then $A + B \succeq C + D$. 
	\end{enumerate}
	\end{lemma}
\end{proof}
